Title

### 2016-05-31 paper/sections/Overview.tex
Split

\begin{lstlisting}
interface Circuit extends Init.Circuit {
  ... // wellSized declaration
}
interface Beside extends Circuit, Init.Beside {
  Circuit _c1(); Circuit _c2(); // type refinements
  ... // wellSized implementation
}
\end{lstlisting}
Interfaces from base families of the same name will be put after \texttt{extends} clause and the
interface hierarchy of \texttt{Circuit} is preserved in the extended family.
Moreover, \name re-declare getters from the base \texttt{Beside} in the extended
\texttt{Beside} so that their return types are refined to be the new
\texttt{Circuit}.

@@

To add these two new constructs to \dsl, we can declare two class-like interfaces \texttt{Above} and
\texttt{Stretch} that extends \texttt{Circuit} with \texttt{width} and
\texttt{wellSized} implemented

\lstinputlisting[linerange=56-76]{../src/paper/sec3/Circuit.java}%APPLY:DEPENDENT
Definitions of \texttt{wellSized} for the new cases make it a dependent interpretation, as they
rely on the \texttt{width} method for calculating the width of a circuit.

%Since \texttt{Circuit} in \texttt{Dependent} family extends the one from
%\texttt{Init}, we can simply call \texttt{width} method on a
%\texttt{Circuit} object when the width of a circuit is needed in the definition
%of \texttt{wellSized}.

@@

\lstinputlisting[linerange=98-130]{../src/paper/sec3/Circuit.java}%APPLY:CONTEXT_SENSITIVE

@@

Some definitions of helper methods are omitted for space reason.
Their functionalities are: \texttt{lzw} stands for 'long zip with', which takes two lists and a binary operator for
combining elements on the same position; if one list is shorter then the
remaining elements of the other are appended to the result list; \texttt{concat}
concatenates two lists with the first tail connected the second head;
The indices of wires are calculated by accumulating the sum of the list \texttt{\_ns} using the \texttt{scanl1}.

@@

\subsection{Interpretation Combination}
One appealing feature that \name approach provides is that we can modularly
merge interpretations defined for the same data structure together.
This is done through from different families
together using multiple interface inheritance.

@@

\lstinputlisting[linerange=161-163]{../src/paper/sec3/Circuit.java}%APPLY:MERGE
Simply defining a new family \texttt{Merge} that extends other families we want
to combine. \name will implicitly re-declare all the interfaces and inject the
inheritance relationships. For example, the implicit redeclaration of
\texttt{Circuit} looks like this:

@@

\begin{comment}
\subsection{Parametrized interpretations}
\subsection{Implicitly Parametrized interpretations}
\subsection{Modular Interpretations}

@@

\lstinputlisting[linerange=168-180]{../src/paper/sec3/Circuit.java}%APPLY:INSTRUMENT
% TODO: not implemented yet
Family polymorphism on only gives more safety on the client code but also helps
language implementers catch bug early.
For example, if one forgets to implement, say cases from \texttt{Family}, in
\texttt{Semantics}, she would get warned they have not implemented the
\texttt{wellSized} method because class-like interfaces should not contain any
unimplemented methods except for getters.
These errors are captured by automatically re-declaring members with inheritance relationships.
%The \texttt{of} method is  returns an instance of an anonymous class
%that implements the interface with all getters implemented and its instance is returned.
\end{comment}

>>>>

\begin{lstlisting}
interface Circuit extends Init.Circuit {
  ... // wellSized declaration
}
interface Beside extends Circuit, Init.Beside {
  Circuit _c1(); Circuit _c2(); // type refinements
  ... // wellSized implementation
}
\end{lstlisting}
Interfaces from base families of the same name will be put after \texttt{extends} clause and the
interface hierarchy of \texttt{Circuit} is preserved in the extended family.
Moreover, \name re-declare getters in the extended \texttt{Beside} so that their return types are refined to be the new \texttt{Circuit}.

@@

Adding new constructs in \name is easy: just we declare new class-like
interfaces in an extended family:
\lstinputlisting[linerange=56-69]{../src/paper/sec3/Circuit.java}%APPLY:SYNTAX
Only definitions of the new constructs \texttt{Above} and \texttt{Stretch} are given.
Their peer constructs and \texttt{Circuit} are implicitly re-declared by \name,
e.g. \texttt{Fan}:

\begin{lstlisting}
interface Fan extends Init.Fan {}
\end{lstlisting}

Not arbitrary circuits can be combined using \texttt{Above} and \texttt{Stretch}.
We hence define the \texttt{wellSized} method for these two new constructs to
verify the constraints they imply:
\lstinputlisting[linerange=73-85]{../src/paper/sec3/Circuit.java}%APPLY:DEPENDENT

Definitions of \texttt{wellSized} for the extended cases make it a dependent interpretation, as they
rely on another method defined on the \texttt{Circuit}, \texttt{width}, for calculating the width of a circuit.

Here, we show yet another appealing feature of \name - interpretation combination.
The \texttt{Dependent} family combines two base families

merge interpretations defined for the same data structure together.
%Since \texttt{Circuit} in \texttt{Dependent} family extends the one from
%\texttt{Init}, we can simply call \texttt{width} method on a
%\texttt{Circuit} object when the width of a circuit is needed in the definition
%of \texttt{wellSized}.

@@

\lstinputlisting[linerange=107-139]{../src/paper/sec3/Circuit.java}%APPLY:CONTEXT_SENSITIVE

@@

Some definitions of helper methods are omitted for space reason.
Their functionalities are: \texttt{lzw} stands for 'long zip with', which takes two lists and a binary operator for
combining elements of the same position and if one list is shorter then the
remaining elements of the other are appended to the result list; \texttt{concat}
concatenates two lists with the first tail connected the second head;
The indices of wires are calculated by accumulating the sum of the list \texttt{\_ns} using the \texttt{scanl1}.

@@

\begin{comment}
\subsection{Interpretation Combination}
One appealing feature that \name approach provides is that we can modularly
merge interpretations defined for the same data structure together.
This is done through from different families
together using multiple interface inheritance.

@@

\lstinputlisting[linerange=170-172]{../src/paper/sec3/Circuit.java}%APPLY:MERGE
Simply defining a new family \texttt{Merge} that extends other families we want
to combine. \name will implicitly re-declare all the interfaces and inject the
inheritance relationships. For example, the implicit redeclaration of
\texttt{Circuit} looks like this:

@@

\subsection{Parametrized interpretations}
\subsection{Implicitly Parametrized interpretations}
\subsection{Modular Interpretations}

@@

\lstinputlisting[linerange=177-189]{../src/paper/sec3/Circuit.java}%APPLY:INSTRUMENT
% TODO: not implemented yet
Family polymorphism on only gives more safety on the client code but also helps
language implementers catch bug early.
For example, if one forgets to implement, say cases from \texttt{Family}, in
\texttt{Semantics}, she would get warned they have not implemented the
\texttt{wellSized} method because class-like interfaces should not contain any
unimplemented methods except for getters.
These errors are captured by automatically re-declaring members with inheritance relationships.
%The \texttt{of} method is  returns an instance of an anonymous class
%that implements the interface with all getters implemented and its instance is returned.
\end{comment}
